Benefits and risks of diversification for individual fishers

### 2017-07-07 portfolio/text/anderson-etal-rev-pfx.tex
Add financial risk to abstract

% 250:
\begin{abstract}
Individuals relying on the extraction of natural resources for their livelihood
face high levels of income variability driven by a mix of environmental,
biological, management, and economic factors. Key to managing these industries
is identifying how regulatory actions and individual behaviour affect income
variability and risk and, by extension, economic stability and the sustainable use of
natural resources. In commercial fisheries, communities and vessels fishing a
greater diversity of species have less revenue variability than those fishing
fewer species. However, it is unclear if these benefits extend to the actions of
individual fishers and how year-to-year changes in diversification affect
revenue and revenue variability. Here, we evaluate two axes by which fishers in
Alaska can diversify fishing activities. We show that, despite increasing
specialization over the last 30 years, fishing a set of permits with higher
species diversity reduces individual revenue variability and fishing an
additional permit is associated with higher revenue and lower variability.
However, increasing species diversity within the constraints of existing permits
has a fishery-dependent effect on revenue and is usually (87\% probability)
associated with increased revenue uncertainty the following year. Our results
demonstrate that the most effective option for individuals to decrease revenue
variability is to participate in additional or more diverse fisheries. However,
this option is expensive, often limited by regulations such as catch share
programs, and consequently unavailable to many individuals. With increasing
climatic variability it will be particularly important that individuals relying
on natural resources for their livelihood have effective strategies to reduce
income variability.
% (`r g2_dens`% probability)
\end{abstract}

@@

\noindent Again, \(S_{i,t}\) and \(I_{i,t}\) represent, respectively, the log
ratio of species diversity from year-to-year and an indicator variable for
increasing or decreasing species diversity. We exponentiate the equation to
ensure all scale parameters, \(\sigma_{i,t}\), are positive. Residuals from
the mean component of our model clearly show a ``V''-shaped pattern, which the
variance component of our model can capture (Fig.~S\figresid). Furthermore,
the downside residuals (year-individual data points with lower than expected
revenue) appear qualitatively similar to the complete set of residuals (upside
and downside) (Fig.~S\figresiddownside). Therefore, it seemed appropriate to
model variability as a proxy for revenue risk. Even though individual upward
spikes in revenue may be desirable and would be reflected by increased revenue
variability, increases in average revenue variability are unlikely to be
desirable.

>>>>

% 250:
\begin{abstract}

Individuals relying on the extraction of natural resources for their livelihood
face high levels of income variability driven by a mix of environmental,
biological, management, and economic factors. Key to managing these industries
is identifying how regulatory actions and individual behaviour affect income
variability, financial risk, and, by extension, the economic stability and the
sustainable use of natural resources. In commercial fisheries, communities and
vessels fishing a greater diversity of species have less revenue variability
than those fishing fewer species. However, it is unclear if these benefits
extend to the actions of individual fishers and how year-to-year changes in
diversification affect revenue and revenue variability. Here, we evaluate two
axes by which fishers in Alaska can diversify fishing activities. We show that,
despite increasing specialization over the last 30 years, fishing a set of
permits with higher species diversity reduces individual revenue variability and
fishing an additional permit is associated with higher revenue and lower
variability. However, increasing species diversity within the constraints of
existing permits has a fishery-dependent effect on revenue and is usually (87\%
probability) associated with increased revenue uncertainty the following year.
Our results demonstrate that the most effective option for individuals to
decrease revenue variability is to participate in additional or more diverse
fisheries. However, this option is expensive, often limited by regulations such
as catch share programs, and consequently unavailable to many individuals. With
increasing climatic variability it will be particularly important that
individuals relying on natural resources for their livelihood have effective
strategies to reduce financial risk.

% (`r g2_dens`% probability)
\end{abstract}

@@

\noindent Again, \(S_{i,t}\) and \(I_{i,t}\) represent, respectively, the log
ratio of species diversity from year-to-year and an indicator variable for
increasing or decreasing species diversity. We exponentiate the equation to
ensure all scale parameters, \(\sigma_{i,t}\), are positive. Residuals from
the mean component of our model clearly show a ``V''-shaped pattern, which the
variance component of our model can capture (Fig.~S\figresid). Furthermore,
the downside residuals (year-individual data points with lower than expected
revenue) appear qualitatively similar to the complete set of residuals (upside
and downside) (Fig.~S\figresiddownside). Therefore, it seemed appropriate to
model variability as a proxy for revenue risk. Ideally, we would model
a more direct measure of risk such as the probability of bankruptcy from low
revenue; however, data on costs and other sources of income were not available.
